\bf Replication Paper

### 2021-11-29 rCode/Draft.Rmd
tweak
tables and stats

---
title: '\bf Replication Paper'
author: 'Catherine Darin and Zagreb Mukerjee'
date: 'Released: \today'
fontsize: 12pt
output:
  pdf_document: default
urlcolor: red
header-includes:
  - \usepackage{bm}
---

@@

```{r setup, echo=F}
library(tidyverse)
```

@@

## Figures
```{r,  echo=F}
regResultList <- readRDS("../regresults.rds")

@@

### descriptive statistics

@@

@@

## Future steps

>>>>

---
title: '\bf Replication Paper'
author: 'Catherine Darin and Zagreb Mukerjee'
date: '\today'
fontsize: 12pt
output:
  pdf_document: default
urlcolor: red
header-includes:
  - \usepackage{bm}
---

\renewcommand{\arraystretch}{1.1}
\renewcommand{\topfraction}{.85}
\renewcommand{\bottomfraction}{.7}
\renewcommand{\textfraction}{.15}
\renewcommand{\floatpagefraction}{.66}
\setcounter{topnumber}{3}
\setcounter{bottomnumber}{3}
\setcounter{totalnumber}{4}

@@

```{r setup, echo=F, message = F, warning= F}
library(tidyverse)
library(stargazer)
library(sandwich)
library(lmtest)
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
```

@@

### Descriptive Statistics
```{r,  echo=F}
descriptiveData <-  readRDS("../tableData.rds")

knitr::kable(descriptiveData$tableOurs,
             caption = "Manufacturing Job Changes 2012-2015",
             booktabs = TRUE, digits = 2, format = 'latex')  %>%
  kable_styling(latex_options = c("hold_position", "scale_down"))

knitr::kable(descriptiveData$table04,
             caption = "Manufacturing Job Changes 2004-2015",
             booktabs = TRUE, digits = 2, format = 'latex')  %>%
  kable_styling(latex_options = c("hold_position", "scale_down"))

@@

## Figures

@@

```{r,  echo=F, message = F, results = "asis"}

regResultList <- readRDS("../regresults.rds")

rownames(regResultList$secondStageModelNetCA$coefficients )[rownames(regResultList$secondStageModelNetCA$coefficients)=="firstStageModelNetCA$fitted.values"] <-  "Manufacturing Layoffs"
rownames(regResultList$secondStageModelNetC$coefficients )[rownames(regResultList$secondStageModelNetC$coefficients)=="firstStageModelNetC$fitted.values"] <-  "Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetCA$coefficients )[rownames(regResultList$secondStageModelWNetCA$coefficients)=="firstStageModelWNetCA$fitted.values"] <-  "White Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetC$coefficients )[rownames(regResultList$secondStageModelWNetC$coefficients)=="firstStageModelWNetC$fitted.values"] <-  "White Manufacturing Layoffs"

rownames(regResultList$secondStageModelWNetCA$coefficients 
)[rownames(regResultList$secondStageModelWNetCA$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetC$coefficients
)[rownames(regResultList$secondStageModelWNetC$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"

rownames(regResultList$secondStageModelNetCA$beta )[rownames(regResultList$secondStageModelNetCA$beta) =="firstStageModelNetCA$fitted.values"] <-  "Manufacturing Layoffs"
rownames(regResultList$secondStageModelNetC$beta )[rownames(regResultList$secondStageModelNetC$beta)=="firstStageModelNetC$fitted.values"] <-  "Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="firstStageModelWNetCA$fitted.values"] <-  "White Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="firstStageModelWNetC$fitted.values"] <-  "White Manufacturing Layoffs"

rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"

names(regResultList$rseNetCA_2)[1] <- "Manufacturing Layoffs"
names(regResultList$rseNetC_2)[1] <- "Manufacturing Layoffs"
names(regResultList$rseWNetCA_2)[1] <- "White Manufacturing Layoffs"
names(regResultList$rseWNetC_2)[1] <- "White Manufacturing Layoffs"

names(regResultList$rseWNetCA_2)[names(regResultList$rseWNetCA_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
names(regResultList$rseWNetC_2)[names(regResultList$rseWNetC_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"

stargazer(regResultList$secondStageModelNetCA,
          regResultList$secondStageModelNetC,
          regResultList$secondStageModelWNetCA,
          regResultList$secondStageModelWNetC,
          se = list(
            regResultList$rseNetCA_2,
            regResultList$rseNetC_2,
            regResultList$rseWNetCA_2,
            regResultList$rseWNetC_2
          ),
          title = "Effect of Manufacturing Layoffs on Democratic Vote Share",
          dep.var.labels = "Change in Share (2012-2016)",
          omit.stat = c("rsq","ser"),
          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
          add.lines = list(
            c("Controls For White Share/Service Layoffs", "No", "Yes", "No", "Yes")
          ),
          digits = 2,
          type = "latex"
)

```{r,  echo=F, message = F, results = "asis"}

rownames(regResultList$secondStageModelNetC04A$coefficients )[rownames(regResultList$secondStageModelNetC04A$coefficients)=="firstStageModelNetC04A$fitted.values"] <-  "Manufacturing Layoffs"
rownames(regResultList$secondStageModelNetC04$coefficients )[rownames(regResultList$secondStageModelNetC04$coefficients)=="firstStageModelNetC04$fitted.values"] <-  "Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetC04A$coefficients )[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="firstStageModelWNetC04A$fitted.values"] <-  "White Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetC04$coefficients )[rownames(regResultList$secondStageModelWNetC04$coefficients)=="firstStageModelWNetC04$fitted.values"] <-  "White Manufacturing Layoffs"

rownames(regResultList$secondStageModelWNetC04A$coefficients
)[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetC04$coefficients
)[rownames(regResultList$secondStageModelWNetC04$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"

rownames(regResultList$secondStageModelNetC04A$beta )[rownames(regResultList$secondStageModelNetC04A$beta) =="firstStageModelNetC04A$fitted.values"] <-  "Manufacturing Layoffs"
rownames(regResultList$secondStageModelNetC04$beta )[rownames(regResultList$secondStageModelNetC04$beta)=="firstStageModelNetC04$fitted.values"] <-  "Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="firstStageModelWNetC04A$fitted.values"] <-  "White Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="firstStageModelWNetC04$fitted.values"] <-  "White Manufacturing Layoffs"

rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"

names(regResultList$rseNetC04A_2)[1] <- "Manufacturing Layoffs"
names(regResultList$rseNetC04_2)[1] <- "Manufacturing Layoffs"
names(regResultList$rseWNetC04A_2)[1] <- "White Manufacturing Layoffs"
names(regResultList$rseWNetC04_2)[1] <- "White Manufacturing Layoffs"

names(regResultList$rseWNetC04A_2)[names(regResultList$rseWNetC04A_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
names(regResultList$rseWNetC04_2)[names(regResultList$rseWNetC04_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"

stargazer(regResultList$secondStageModelNetC04A,
          regResultList$secondStageModelNetC04,
          regResultList$secondStageModelWNetC04A,
          regResultList$secondStageModelWNetC04,
          se = list(
            regResultList$rseNetC04A_2,
            regResultList$rseNetC04_2,
            regResultList$rseWNetC04A_2,
            regResultList$rseWNetC04_2
          ),
          title = "Effect of Manufacturing Layoffs on Democratic Vote Share (since 2004)",
          dep.var.labels = "Change in Share (2016-2012)",
          omit.stat = c("rsq","ser"),
          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
          add.lines = list(
            c("Controls For White Share/Service Layoffs", "No", "Yes", "No", "Yes")
          ),
          digits = 2,
          type = "latex"
)

@@

## Potential Future Work
